

```markdown
---

``r 'r chunk_reveal("wrangle")'``
``` 


````markdown
```{r wrangle, include = FALSE}`r ''`
cars %>% 
  mutate(high_speed = 
           speed > 10) %>% 
  mutate(high_dist = 
           dist > 20) ->
cars_mod
```
````

---

```{r, comment = ""}
cat("---\n\n```{r wrangle, include = FALSE}
cars %>% 
  mutate(high_speed = 
           speed > 10) %>% 
  mutate(high_dist = 
           dist > 20) ->
cars_mod
```\n\n---")
```




```{r, eval = F}
library(tidyverse)
readLines("https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/most-features/skeleton/skeleton.Rmd", skipNul = F) ->
lines  

lines %>% 
  str_replace_all(" ", "~~") %>% 
  data.frame(line = .) %>% 
  mutate(original = str_replace_all(line, "~~", " ")) %>% 
  # mutate(start_chunk = str_detect(line, "```\\{r")) %>% 
  # mutate(mod = ifelse(start_chunk, 
  #                     paste0("````markdown\n", line, 
  #                            "`r ''`"), "")) %>% 
  # mutate(end_chunk = str_detect(line, "```$")) %>% 
  # # filter(start_chunk) %>% 
  # mutate(in_line = str_detect(line, "^`r")) %>% 
  # mutate(mod = ifelse(end_chunk, 
  #                     paste0(line, "\n````"),
  #                     "")) %>% 
  mutate(slide_break = str_detect(line, "^---$")) %>% 
  mutate(slide = cumsum(slide_break)) %>% 
  filter(!slide_break) %>% 
  group_by(slide) %>% 
  summarize(slide_content = paste0(line, collapse = "\n")) %>% 
  pull() %>% 
  str_replace_all("~~", " ") %>% 
  paste0("---\n",., "\n---\nclass: inverse\n\n", 
         "```{r, comment = '', echo = F, return = 'asis'}\ncat('"````, 
         str_replace_all(str_replace_all(., "\'", "\\\\'"), "\n", "\n\\\\n ") , 
         "')\n```") %>% 
  paste0(collapse = "\n---\n") %>% 
  writeLines(con = "test_out.Rmd")  

"```{r, comment = ''}\ncat("
")
```"
```


```{r}
  

ifelse(T, paste0("hi", "`r ''`"), "")
str_detect("`r", "`r")
```

