---
title: "Reynolds Lab"
subtitle: ""
author: ""
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      seal: FALSE
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---




```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = T)
options(knitr.duplicate.label = "allow")
library(flipbookr)
library(tidyverse)
```

class: inverse
background-image: url(https://images.unsplash.com/photo-1568526381923-caf3fd520382?ixlib=rb-1.2.1&ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&auto=format&fit=crop&w=1500&q=80)


# Reynolds lab for statistical learning and communication



# Current and previous affiliates

- Conner Surrency
-



# {flipbookr}

- new reveal modes
- python
- embedding


---

# We worked on new functionality


```{r, eval = F}
flipbookr::chunk_expand(chunk_name = "chunk", break_type = "replace", 
                        replace = "green",
                        replacements = c("green", "red"),
                        display_type = c("md", "output", "output_lag"), 
                        md = c("first ...", "then ,,"),
                        chunk_options = "fig.width = 6, fig.height = 3",
                        title = "my flipbook",
                        lang = "python"
                        )
```


---

`r chunk_reveal("features", display_type = "code")`


```{r features, eval = F, echo = F}
download.file("https://raw.githubusercontent.com/EvaMaeRey/flipbookr/master/inst/rmarkdown/templates/most-features/skeleton/skeleton.Rmd", 
              destfile = "flipbookr_features.Rmd")
rmarkdown::render("flipbookr_features.Rmd")
```


---
class: inverse, right
background-image: url(https://images.unsplash.com/photo-1559533352-2a5655ff467b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1500&q=80)
background-size: cover

--

# {[ggquiet](https://github.com/EvaMaeRey/ggquiet)}



---

`r chunk_reveal("ggquiet", break_type = "user")`



```{r ggquiet, include=F}
cars %>% 
  ggplot() + 
  aes(x = speed) +
  aes(y = dist) +
  geom_blank() + 
  labs(title = "What a great title") +
  theme_minimal(base_size = 18) +
  theme(plot.title.position = "plot") + #BREAK
  ggquiet::theme_quiet() + #BREAK
  ggquiet:::x_axis_adjust("black", alpha = .8) + #BREAK
  ggquiet:::y_axis_adjust("black", alpha = .8) + #BREAK
  ggquiet:::titles_adjust("black", alpha = .8) + #BREAK
  geom_point(data = . %>% slice(20),
             size = 5) + #BREAK
  geom_point(size = 5) #BREAK
```



---

`r chunk_reveal("ggquiet2", break_type = "user", display_type = "output", chunk_options = "fig.width = 10, fig.height = 7, fig.align = 'center'", title = "### Now w/ display of output only I present it ... *quietly*! <br>")`

```{r ggquiet2, include=F}
cars %>% 
  ggplot() + 
  aes(x = speed) +
  aes(y = dist) +
  geom_blank() + 
  labs(title = "What a great title") +
  theme_minimal(base_size = 18) +
  theme(plot.title.position = "plot") +
  ggquiet::theme_quiet() + #BREAK
  ggquiet:::x_axis_adjust("black", alpha = .8) + #BREAK
  ggquiet:::y_axis_adjust("black", alpha = .8) + #BREAK
  ggquiet:::titles_adjust("black", alpha = .8) + #BREAK
  geom_point(data = . %>% slice(20),
             size = 5) + #BREAK
  geom_point(size = 5) + #BREAK
  aes(color = speed) +
  scale_color_viridis_c(option = "magma") +
  theme(legend.position = c(.2,.8),
        legend.direction = "horizontal",
        legend.background = element_rect(fill = alpha("black", alpha = 0), 
                                         color = alpha("black", alpha = 0))) +
  geom_point(color = "black", size = 5) + #BREAK
  geom_point(size = 5) #BREAK
```


---
class: inverse
background-image: url(https://images.unsplash.com/photo-1572291720677-d8d28ac52a5b?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1556&q=80)

--

# {ggxmean}

---

`r chunk_reveal("ggxmean")`


```{r ggxmean, include=F}
library(ggxmean) #BREAK
mtcars %>% 
  ggplot() + 
  aes(x = wt) + 
  aes(y = mpg) +
  geom_point() + #BREAK
  geom_xmean(linetype = "dashed") + #BREAK
  geom_xvlines(alpha = .2) + #BREAK
  aes(color = as_factor(cyl)) + #BREAK
  facet_grid(rows = vars(cyl)) #BREAK
```

---
class: right, inverse
background-image: url(https://images.unsplash.com/photo-1517327832109-76f52a6c5eab?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1500&q=80)
background-size: contain

--

# flipbookr::text_reveal()

---
class: bottom, center, inverse
background-image: url(https://images.unsplash.com/photo-1578161467910-11ca4025aa0e?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1500&q=80)
background-size: contain

--

# flipbookr::embed_flipbook()


---

```{r embedding, include = F}
ggplot(cars) +
  aes(speed, dist) +
  geom_point(size = 5) +
  aes(color = speed) + 
  scale_color_viridis_c(option = "magma")
```

```{r}
flipbookr::embed_flipbook("embedding", 
                          use_share_again = T,
                          use_embed_xaringan = T
                          )
```



---
class: inverse, bottom
background-image: url(https://images.unsplash.com/photo-1577635515158-dcce4789c8fb?ixlib=rb-1.2.1&ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&auto=format&fit=crop&w=751&q=80)
background-size: cover


# {doublecrochet}



---

`r chunk_reveal("doublecrochet", display_type = "code")`


```{r doublecrochet, eval = F, echo = F}
doublecrochet::crochet("flipbookr_features.Rmd")
rmarkdown::render("flipbookr_features_double.Rmd")
```


---

Compare the rendered original and the double crocheted version, or check out the full double crocheted version [here](flipbookr_features_double.html).

```{r, out.width="46%"}
knitr::include_url(c("flipbookr_features.html", "flipbookr_features_double.html"))
```



---
class: inverse
background-image: url(https://images.unsplash.com/photo-1503694978374-8a2fa686963a?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1050&q=80)
background-size: cover

# {xaringanPrinter}


---
class: inverse
background-image: url(https://images.unsplash.com/photo-1588429750683-c423e17a10c0?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=634&q=80)
background-size: contain

# {viztoc}


---
